---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview
`binomial` is a minimal package that provides functions to get the probability given trials, success time and provides the functions to get summary measures like mean, variance, etc. It also generates some plots to show the probability and cumulative probability.

* `plot()` method plot probablity of each success and cumulative probablities.
* `summary()` method for get the summary of the parameters and measures

# Usage
```{r}
library(binomial)
# get the total combination number
bin_choose(5, 1:3)
#get the probability
bin_probability(5,trials = 10, prob = 0.5)

# get the distribution and plot the distribution
bin_distribution(trials = 5, prob = 0.5)
plot(bin_distribution(trials = 5, prob = 0.5))

# get the cumulative probabilities
bin_cumulative(trials = 5, prob = 0.5)
plot(bin_cumulative(trials = 5, prob = 0.5))

# get the variable and print the summary thing
bin_variable(trials = 10, p = 0.3)
summary(bin_variable(trials = 10, p = 0.3))


# get functions of measures
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)

```
```{r}
summary(bin_variable(trials = 10, p = 0.3))
```

